Staged Abstract Interpreters

### 2019-08-16 paper/30_stageconc.tex
tweak for latexdiff

The IR nodes are manipulated by the LMS passes and finally generated to
next-stage Scala code. To generate code, LMS provides an \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{emitNode} method for
programmers to control what is generated for each kind of node. Here we have
matched \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{IRCompiledClo} and \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{IRApClo} and will generate definitions for them.
For compiled closures, we put the function \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{f} and its accompanying syntactic term
and environment to its next-stage value representation \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{CompiledClo}. For
applications, we have the knowledge that \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{fun} is a \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{CompiledClo} at the stage,
and it has a callable field \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{f}, so we generate a next-stage function
application \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{f(arg, σ)}. The \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{quote}s are invocations to generate code for the
other next-stage values.
\begin{lstlisting}
override def emitNode(sym: Sym[Any], rhs: Def[Any]) = rhs match {
  case IRCompiledClo(f, λ, ρ) => emitValDef(sym, s"CompiledClo($\textdollar${quote(f)}, $\textdollar${quote(λ)}, $\textdollar${quote(ρ)})")
  case IRApClo(rator, rand, σ) => emitValDef(sym, s"$\textdollar$rator.f($\textdollar${quote(rand)}, $\textdollar${quote(σ)})")
  ...
}
\end{lstlisting}

>>>>

The IR nodes are manipulated by the LMS passes and finally generated to
next-stage Scala code. To generate code, LMS provides an \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{emitNode} method for
programmers to control what is generated for each kind of node. Here we have
matched \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{IRCompiledClo} and \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{IRApClo} and will generate definitions via \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{emitValDef} for them.
For compiled closures, we put the function \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{f} and its accompanying syntactic term
and environment to its next-stage value representation \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{CompiledClo}. For
applications, we have the knowledge that \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{fun} is a \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{CompiledClo} at the stage,
and it has a callable field \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{f}, so we generate a next-stage function
application \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{f(arg, σ)}. The \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{quote}s are invocations to generate code for the
other next-stage values.
\begin{lstlisting}
override def emitNode(sym: Sym[Any], rhs: Def[Any]) = rhs match {
  case IRCompiledClo(f, λ, ρ) => emitValDef(sym, s"CompiledClo($\textdollar${quote(f)}, $\textdollar${quote(λ)}, $\textdollar${quote(ρ)})")
  case IRApClo(rator, rand, σ) => emitValDef(sym, s"$\textdollar$rator.f($\textdollar${quote(rand)}, $\textdollar${quote(σ)})")
  ...
}
\end{lstlisting}
